Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-31 notes/gamma-sensitivity-proof/main.tex
rename file prove the gamma smooth sensitivity

\begin{definition}

$S(\dataobs)$ is the $\gamma -$smooth sensitivity of data set $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:

\begin{equation}
\label{eq_gamma_smooth}
|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma.
\end{equation}
\end{definition}

\begin{thm}
\label{thm_gamma_smooth}
$S_\beta(\dataobs)$ is $\gamma -$smooth sensitivity for $\hellinger(\bysinfer(\dataobs),-)$ if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.

@@

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $2\epsilon$-differential privacy in Beta-binomial system.
\end{lem}

@@

  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\nomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\nomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

>>>>

\begin{definition}
Given data set $\dataobs$, $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:

\begin{equation}
\label{eq_gamma_smooth}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation}
\end{definition}

\begin{thm}
\label{thm_gamma_smooth}
$S_\beta(\dataobs)$ is $\gamma -$smooth sensitivity for $\hellinger(\bysinfer(\dataobs),-)$ if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma \cdot d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.
For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:

By Definition \ref{eq_smooth}:
\begin{equation*}
\begin{split}
S(\dataobs) 
& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
\frac{1}{S(\dataobs)} 
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
\end{split}
\end{equation*}

Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:

\begin{equation*}
\begin{split}
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}

@@

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $2\epsilon$-differential privacy.
\end{lem}

@@

  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
